### 2016-11-12 thesis/intro/intro.tex
tmp commit

\gls{pyy} is a gut hormone that is secreted postprandially, and it is released at levels proportional to the calorie content of the meal (original citation, Adrian1985 gastroenterology).
\gls{y2r} is an inhibitory presynaptic receptor that is highly expressed in the \gls{npy}/\gls{agrp} neuron, and is the target of the \gls{pyy} hormone \citep{Batterham2002}.
\citet{Batterham2002} showed that \gls{pyy} decreased the expression of \gls{npy} in the \gls{npy}/\gls{agrp} neuron, and activated the \gls{pomc}/\gls{cart} neuron by membrane depolarisation.
The two mechanisms of \gls{pyy} produces an anorexogenic signal and encourages the individual to stop eating.

@@

There are many genetic evidence of obesity being caused by individual-level factors that makes some individuals more predisposed (right word??) to obesity than others (citation).

@@

>>>>

\gls{pyy} is a gut hormone that is secreted postprandially, and it is released at levels proportional to the calorie content of the meal (original citation, Adrian1985 gastroenterology).
\gls{y2r} is an inhibitory presynaptic receptor that is highly expressed in the \gls{npy}/\gls{agrp} neuron, and is the target of the \gls{pyy} hormone \citep{Batterham2002}.
\citet{Batterham2002} showed that \gls{pyy} decreased the expression of \gls{npy} in the \gls{npy}/\gls{agrp} neuron, and activated the \gls{pomc}/\gls{cart} neuron by membrane depolarisation.
The two mechanisms of \gls{pyy} produces an anorexogenic signal and encourages the individual to stop eating.\\

\noindent
When any one of these neurons, neuropeptides, hormones or its corresponding receptors become defective, it can lead to some form of eating disorder.
Therefore the roles of these neurons, neuropeptides, and hormones are crucial for healthy diet and body weight maintenance.

@@

There are many evidence of obesity being caused by individual-level genetic factors that make some individuals more predisposed to obesity than others (citation).
Generally speaking, there are two classes of genetic-driven obesity: monogenic obesity and polygenic obesity \citep{Moustafa2013}. \\

\noindent
Monogenic obesity is where a single mutation in one of the genes that is directly involved in the obesity pathway causes severe obesity in the individual.
Since these mutations are usually directly related to the key neurons/neuropeptides/hor\-mones that were mentioned earlier (\cref{sub:physiological_mechanism_of_obesity}), the resulting phenotype from the mutation causes severe early-onset obesity.
However, although these mutations cause a devastating effect on the individual, these mutations occur very rarely in the population.
With that said though, the identification of these mutations have shed light on the mechanisms in which obesity is developed and it is worth mentioning some of these mutations to highlight the importance of the components involved in the obesity pathway.

The first mutation that should be mentioned is in the leptin gene.
\\

@@

\noindent
Polygenic obesity is where 
\\
